Growth model analysis 3spp WB

### 2019-03-05 MS_Analysis_3spp_4rivers_Patterns_from 2spp.Rmd
updated figures

# Has mean size changed over time?
means <- 
  cd %>% mutate( age = year - cohort ) %>%
    filter( ageInSamples %in% 1:10, age < 3, year < 2016, area %in% c('inside','trib') ) %>%
    group_by(species,riverOrdered,ageInSamples,year,season,age) %>%
    summarize(meanLen = mean(observedLength,na.rm = TRUE),
              sdLen = sd(observedLength,na.rm = TRUE),
              meanGR = mean(grLength,na.rm = TRUE),
              sdGR = sd(grLength,na.rm = TRUE)
              )

@@

# do increases (slopes) increase over age? Yes
ggplot(lenSlopesTidy %>% filter(), aes((ageInSamples),estimate, color=speciesGG)) +
  geom_point( size = 3) +
  geom_smooth(method='lm', se=FALSE) +
  scale_x_continuous(breaks = 1:10, labels = c(0,0,1,1,1,1,2,2,2,2)) +
  labs( x = "Age", y = "Slope of mean body length over years" ) +
  theme_publication() +
  scale_color_grey(start = 0.15, end = 0.75) +
  facet_wrap(~riverOrdered)

@@

@@

>>>>

# Has mean size changed over time?
means <- 
  cd %>% mutate( age = year - cohort ) %>%
    filter( ageInSamples %in% 1:10, age < 3, year < 2016, area %in% c('inside','trib'), enc == 1) %>%
    group_by(species,riverOrdered,ageInSamples,year,season,age) %>%
    summarize(meanLen = mean(observedLength,na.rm = TRUE),
              sdLen = sd(observedLength,na.rm = TRUE),
              meanGR = mean(grLength,na.rm = TRUE),
              sdGR = sd(grLength,na.rm = TRUE),
              n = n()
              )

@@

# do increases (slopes) increase over age? Yes
ggplot(lenSlopesTidy %>% filter(!(riverOrdered == 'wb mitchell' & ageInSamples > 8)), aes((ageInSamples),estimate, color=speciesGG)) +
  geom_point( size = 3) +
  geom_smooth(method='lm', se=FALSE) +
  scale_x_continuous(breaks = 1:10, labels = c(0,0,1,1,1,1,2,2,2,2)) +
  labs( x = "Age", y = "Slope of mean body length over years" ) +
  theme_publication() +
  scale_color_grey(start = 0.15, end = 0.75) +
  facet_wrap(~riverOrdered)

@@

# just bkt
ggplot(lenSlopesTidy %>% filter(!(riverOrdered == 'wb mitchell' & ageInSamples > 8), species == 'bkt'), aes((ageInSamples),estimate, color=riverOrdered, shape = riverOrdered)) +
  geom_point( size = 3) +
  geom_smooth(method='lm', se=FALSE) +
  scale_x_continuous(breaks = 1:10, labels = c(0,0,1,1,1,1,2,2,2,2)) +
  labs( x = "Age", y = "Slope of mean body length over years" ) +
  theme_publication()

ggsave(paste0('figures/meanLengthsOverAgeBKT.png'), width = 6, height = 6, units='in')

@@

# just bkt
ggplot(grSlopesTidy %>% filter(!(riverOrdered == 'wb mitchell' & ageInSamples > 8), species == 'bkt'), aes((ageInSamples),estimate, color=riverOrdered, shape = riverOrdered)) +
  geom_point( size = 3) +
  geom_smooth(method='lm', se=FALSE) +
  scale_x_continuous(breaks = 1:10, labels = c(0,0,1,1,1,1,2,2,2,2)) +
  labs( x = "Age", y = "Slope of mean growth rate over years" ) +
  theme_publication()

ggsave(paste0('figures/meanGRsOverAgeBKT.png'), width = 6, height = 6, units='in')
